Assessing MCR Discussion Usefulness using Semantic Similarity

### 2014-07-28 sections/approach.tex
more refactorings

That is, we assume that that the more similar a comment is to the proposed change, the more relevant it is and hence more likely useful.
Conversely, the more dissimilar\footnote{This can be arbitrarily large, thus not simply the opposite of similarity}, the less relevant, and hence less useful.

Given the subjective nature of usefulness, precise classification conditions probably do not exist and so we resort to conditions that indicate a meaningful \emph{likelihood} of classification.
That is, for some degree of similarity a comment is most likely useful, and for some degree of dissimilarity it is most likely not useful.
The key is determining these degrees in a practical and effective manner.
While this representation is straightforward and automatically adjusts to the quality of the data, it has a few drawbacks.

First, we have to accept that some comments cannot be reliably or confidently classified.
We denote these as \emph{undetermined} to differentiate them from comments whose usefulness is \emph{unclear} (i.e. cannot be assessed subjectively).
Secondly, owing to the subjective assessment of usefulness, this representation fundamentally implies supervised classification requiring nontrivial training data to define representative classification sets.
This decreases the cost-effectiveness and limits the practicality of application to projects with a large enough number of comments, where the classification effort saved overcomes the training costs.  
% empirically driven and automatically adapts to the quality the data

@@

>>>>

That is, we assume that that the more similar a comment is to the proposed change, the more relevant it is and hence more likely useful.
Conversely, the more dissimilar\footnote{This can be arbitrarily large, thus not simply the opposite of similarity.}, the less relevant, and hence less useful.

Given the subjective nature of usefulness, precise classification conditions probably do not exist and so we resort to conditions that indicate a meaningful \emph{likelihood} of classification.
That is, for some degree of similarity a comment is most likely useful, and for some degree of dissimilarity it is most likely not useful.
The key is determining these degrees in a practical and effective manner.

@@

% Our proposed approach is empirically driven and automatically adjusts to the quality the data.
While our proposed approach is straightforward and automatically adjusts to the quality of the data, it has a few drawbacks.
First, we have to accept that some comments cannot be reliably or confidently classified.
We denote these as \emph{undetermined} to differentiate them from comments whose usefulness is \emph{unclear} (i.e. cannot be assessed subjectively).
Secondly, owing to the subjective assessment of usefulness, this representation fundamentally implies supervised classification requiring nontrivial training data to define representative classification sets.
This decreases the cost-effectiveness and limits the practicality of application to projects with a large enough number of comments, where the classification effort saved overcomes the training costs.  
% empirically driven and automatically adapts to the quality the data

### 2014-07-28 sections/introduction.tex
lots of change to the paper text.
use enumitems for better research questions styling
Now going through the results.
working on section 3
more refactorings

Because performance of code review has a clear relationship to the quality of software project, many studies have investigated the influencing factors in MCR\cite{Baysal2001,Mcintosh,Beller,Hamasaki2013}.
However, little research exists investigating how the discussion for a proposed change impacts software quality.
Given that most proposed changes are triggered from reviewer comments \cite{Beller}, 
it is possible that reviewers comments can either positively contribute to the proposed changes (i.e. ``\emph{useful}''), or be a discussion which is out of scope (i.e. relatively  ``\emph{useless}''  to the proposed changes). 
Since MCR does not require strict guidelines, checklists, or formal processes, some reviewers tend to look for trivial issues (e.g. coding styles), leaving deeper issues undiscussed \cite{Bacchelli2013a}. This is a concern because a high-degree of useless comments not only fails to contribute to improving quality, but also degrades the cost-effectiveness and perceived utility of MCR.%This is a concern because lack of useful comments can degrade the cost-effectiveness and perceived utility of MCR.

@@

In this paper, we present a text mining approach to assist in classifying the usefulness of comments.
The proposed approach is meant to enable classifying the large amounts of MRC comments, in order to conduct comment and code quality studies, such as those discussed earlier, as manual classification can quickly become an untenable task.
By introducing some automation support based on objective empirical criteria,
our proposed method aims to both reduce effort and increase confidence in classification to a degree that is practical for addressing very large MRC data sets.
%Because usefulness of a comment is not precisely defined and is a subjective qualification, we cannot, and do not intend to fully automate or replace human driven classification.  
Through a case study of Qt project, we address the following research questions:
\begin{description}
\item[RQ1:] Is semantic similarity a good indicator of MCR comment usefulness?\\
\item[RQ2:] Is semantic similarity classification cost-efficient, assurable, and scalable?
\end{description}

Our contributions are as follows:
\begin{itemize}
\item We propose a practical approach to mine natural text of comments in code reviews and classify their usefulness based on using semantic similarity.
\item We investigate relationship between usefulness of comments and semantic similarity.
\item We investigate cost-efficient, assurable and scalable of semantic similarity in large open source project based on actual human effort.
\end{itemize}

>>>>

Because performance of code review has a clear relationship to the quality of software project, many studies have investigated the influencing factors in MCR\cite{Baysal2001,Mcintosh,Beller,Hamasaki2013}.
However, little research exists investigating how the discussion for a proposed change impacts software quality.
Given that most proposed changes are triggered from reviewer comments \cite{Beller}, 
it is possible that reviewers comments can either positively contribute to the proposed changes (i.e. ``\emph{useful}''), or be a discussion which is out of scope (i.e. relatively  ``\emph{useless}''  to the proposed changes). 
Since MCR does not require strict guidelines, checklists, or formal processes, some reviewers tend to look for trivial issues (e.g. coding styles), leaving deeper issues undiscussed \cite{Bacchelli2013a}.
%This is a concern because a high-degree of useless comments not only fails to contribute to improving quality, but also degrades the cost-effectiveness and perceived utility of MCR.
This is a concern because a low-degree of useful comments can degrade the overall quality and perceived utility of MCR.

@@

In this paper, we present a text mining approach to assist in classifying the usefulness of comments.
The proposed approach is meant to enable classifying the large amounts of MRC comments, in order to conduct comment and code quality studies, such as those discussed earlier, as manual classification can quickly become an untenable task.
By introducing some automation support based on objective empirical criteria,
our proposed method aims to both reduce effort and increase confidence in classification to a degree that is practical for addressing very large MRC data sets.
%Because usefulness of a comment is not precisely defined and is a subjective qualification, we cannot, and do not intend to fully automate or replace human driven classification.  
Through a case study of Qt project, we address the following research questions:
\begin{ResearchQuestions}
\item[RQ1:] Is semantic similarity a good indicator of MCR comment usefulness?\\
\item[RQ2:] Is semantic similarity classification cost-efficient, assurable, and scalable?
\end{ResearchQuestions}

Our contributions are as follows:
\begin{itemize}
\item We propose a practical approach to mine natural text of comments in code reviews and classify their usefulness using semantic similarity.
\item We investigate relationship between usefulness of comments and semantic similarity.
\item We investigate cost-efficient, assurable and scalable of semantic similarity in large open source project based on actual human effort.
\end{itemize}
